---
title: "danikue.com demo"
author: 'Danielle Kuehler'
output:
  word_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 4
    fig_width: 6
---

```{r, setup, include=FALSE}
require(mosaic)
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=TRUE,     # display code as typed
  size="small",
  comment=FALSE)   # slightly smaller font for code

library(stargazer)
library(visreg)
library(car)
```

# Example 1
I want to stimate the Cobb-Douglas production funciton $Y=K^{0.5}L^{0.5}\varepsilon$. After taking the log transformation, I can still apply the OLS estimator: $\log(Y)=0.5\log(K)+0.5\log(L)+u$, where $u=log(\varepsilon).$ I first generate $K$ from a log-normal distribution with `meanlog=0` and `sdlog=2`, $L$ from a log-normal distribution with `meanlog=0` and `sdlog=5`, and $\varepsilon$ from a log-normal distribution with `meanlog=0` and `sdlog=1`. The sample size is 100. Then I generate $Y$ using the Cobb-Douglas function, and combine the simulated data into a data.frame.

```{r}
nsample<-100 #samplesize
set.seed(777)
#Generating K
K<-rlnorm(nsample,meanlog=0,sdlog=2)
#Generating L
L<-rlnorm(nsample, meanlog=0,sdlog=5) 
#Generate $\varepsilon$
u<-rlnorm(nsample,meanlog=0,sdlog=1)

#Y using Cobb-Douglas
Y<-sqrt(K)*sqrt(L)*u

#Combining data
mydata<-data.frame(Y,K,L)
```

***
# Example 2
Estimating the Cobb-Douglas production function: $\log(Y)=\beta_K\log(K)+\beta_L\log(L)$ and using `stargazer` to print out the regression on the 95\% confidence interval.

```{r}
result<-lm(formula=log(Y)~-1+log(K)+log(L), data=mydata)
stargazer(result, type='text', ci=TRUE, ci.level=.95, digits=2, decimal.mark=".", report="vcs")
```

We reject the null hypothesis that $\beta_K$ = 0 because $\beta_K$ does not include zero

***
# Example 3
Visualizing the sample production function.

```{r}
visreg<-(result)
visreg2d(result, "K", "L")
```


***
# Example 4
Testing the hypothesis of constant return to scale.

```{r}
#TEST for constant returns to scale
linearHypothesis(result,'log(K)+log(L)=1')
```
Conculsion: Production function has constant returns to scale, proven in test





